Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/abstract.tex
"compared to" => "compared with"

\begin{abstract} 
    The Bayesian optimization algorithm has recently shown promising
    performance for the automated design analog integrated circuits. However,
    the sequential property of Bayesian optimization limits its further
    application. In this paper, a batch bayesian optimization algorithm is
    proposed, the parallelization is realized via a multi-objective ensemble of
    acquisition functions. In each iteration, multiple acquisition functions
    are selected, the multi-objective optimization is performed to search for
    the Pareto front of the acquisition functions, candidate points are then
    sampled from the Pareto front. The proposed method is compared with several
    state-of-the-art batch Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits; the experimental
    results show that the proposed method is competitive compared to the
    state-of-the-art algorithms.
\end{abstract}

>>>>

\begin{abstract} 
    The Bayesian optimization algorithm has recently shown promising
    performance for the automated design analog integrated circuits. However,
    the sequential property of Bayesian optimization limits its further
    application. In this paper, a batch bayesian optimization algorithm is
    proposed, the parallelization is realized via a multi-objective ensemble of
    acquisition functions. In each iteration, multiple acquisition functions
    are selected, the multi-objective optimization is performed to search for
    the Pareto front of the acquisition functions, candidate points are then
    sampled from the Pareto front. The proposed method is compared with several
    state-of-the-art batch Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits; the experimental
    results show that the proposed method is competitive compared with the
    state-of-the-art algorithms.
\end{abstract}

### 2018-02-06 paper/experiments.tex
"compared to" => "compared with"

We also ran the MACE algorithm in sequential mode and compared the EI and LCB
acquisition functions, the sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

@@

The mean convergence plot for the sequential and batch runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared to other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared to the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.

>>>>

We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
acquisition functions, the sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

@@

The mean convergence plot for the sequential and batch runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared with other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared with the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.
